Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-08-09 GNproof.tex
made changes to GNproof according to Karen's comments; removed non-crossing partition reference

In order to exhibit a dependent subset of vertices in $J$, we first define a sequence of sets of propagators by
\[Q_0 = \Prop(j_m), \qquad Q_{l+1} = \Prop(I_i(Q_l))\quad \forall l \geq 0.\]
It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$. Since $\cP$ is finite, the sequence therefore stabilizes in finitely many steps when $Q_{l+1} = Q_l$. Let $Q$ be this set of propagators. We show that $I_i(Q) \cup {j_m}$ is a dependent set because it only supports the propagators in $Q$ but has $|Q|+1$ vertices. Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.

@@

To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [i, j_m]$ ($[i, j_m-1]$ if $l >1$), and when this does not hold. In the first case, non-crossing propagators force $V(q) \subseteq [a_r-1, j_m-1]$.

@@

If $V(p_r) \not \subseteq [i, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$. Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$. It follows that $I_i(p_s) <_i I_i(p_r)$. Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.

@@

Now repeat the argument above with $p_s$ in place of $p_r$. Either $V(p_s)  \subseteq [i, j_m]$, or $V(p_s) \not \subseteq [i, j_m]$. In the first case, $V(q) \subseteq [a_r-1, j_m-1]$. In the secont case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$. Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step.

>>>>

In order to exhibit a dependent subset of vertices in $J$, we first define a sequence of sets of propagators by
\[Q_0 = \Prop(j_m), \qquad Q_{l+1} = \Prop(I_i(Q_l))\quad \forall l \geq 0.\]
It is easily verified that this is an increasing chain of sets: indeed, if $q \in Q_l$ then $I_i(q) \in I_i(Q_l)$, and since $I_i(q)$ is one of the vertices that supports $q$ we must have $q \in \Prop(I_i(Q_l)) = Q_{l+1}$. Since $\cP$ is finite, the sequence therefore stabilizes in finitely many steps when $Q_{l+1} = Q_l$. Let $Q$ be this set of propagators. We show that $I_i(Q) \subseteq \mathcal{P}_{m-1}$. Since $I_i$ assigns a single vertex to each propagator, $|I_i(Q)| = |Q|$. Therefore $I_i(Q) \cup {j_m}$ is a dependent set because it only supports the propagators in $Q$ but has $|Q|+1$ vertices. Thus $J$ is a dependent set, and the Grassmann necklace $(I_1,\dots,I_n)$ constructed from $W$ does indeed define the positroid $M(W)$.

@@

To check that $V(q) \subseteq [a_r-1, j_m-1]$, there are two cases to consider: when $V(p_r) \subseteq [a_r-1, j_m]$ ($[a_r-1, j_m-1]$ if $l >1$), and when this does not hold. In the first case, non-crossing propagators force $V(q) \subseteq [a_r-1, j_m-1]$.

@@

If $V(p_r) \not \subseteq [a_r-1, j_m]$, then there must be some propagator $p_s \in Q_{l-2}\setminus Q_{l-3}$ such that $p_r$ and $p_s$ are both supported on $I_i(p_s) := a_s$. Since $p_r$ is outside $q$ in the $a_r-1$ order, and $q \not\in Q_{l-1}$, $q$ cannot be supported on $I_i(p_s)$. It follows that $I_i(p_s) <_i I_i(p_r)$. Therefore $q$ is inside $p_s$ with respect to $<_{a_s - 1}$ as well.

@@

Now repeat the argument above with $p_s$ in place of $p_r$. Either $V(p_s)  \subseteq [a_s-1, j_m]$, or $V(p_s) \not \subseteq [a_s-1, j_m]$. In the first case, $V(q) \subseteq [a_s-1, j_m-1]$. In the second case, there exists some $p_t \in Q_{l-3}$ with $p_s$ supported on $I_i(p_t)$ and $I_i(p_t) <_i I_i(p_s)$. Since there are finitely many steps this process can take before reaching $Q_0$, and any $p_* \in Q_0  = \Prop(j_m)$ has $j_m$ in its support by definition, this argument eventually terminates with the construction of a propagator constraining the positioning of $q$ as required. This completes the induction step.
